---
title: "CovidPlots"
output: 
    github_document:
        toc: true
        toc_depth: 4
date: '`r format(Sys.time(), "%d %B %Y %I:%M %p %Z")`'
---


```{r, setup, include=FALSE}
knitr::opts_chunk$set(out.width = 4800,  fig.width = 12, fig.asp=0.62,  dev = 'svg') 
knitr::opts_chunk$set(echo = TRUE)
```

## CDC All Deaths by Week
The CDC Flu View website gives weekly deaths by state going back several years. Data entry and reporting lags by many weeks, so the last month or so of deaths will be under-reported

https://gis.cdc.gov/grasp/fluview/mortality.html

```{r, cdc_all_deaths, echo=FALSE, results='hide', message=FALSE,warning=FALSE}
  source("cdc_deaths.r")
  print(p_all_deaths_recent)
  print(p_year_on_year)

```



```{r, get_data, include=FALSE}
    source("nytimes_us_counties.r")
    ca <- getCountiesByChunk ('California', ISOdate(2020,3,1, tz=""), 5,  countyPopulations)
    ny <- getCountiesByChunk ('New+York', ISOdate(2020,3,1, tz=""), 5,  countyPopulations)
    mi <- getCountiesByChunk ('Michigan', ISOdate(2020,3,1, tz=""), 5,  countyPopulations)
    selected <- getSelectedCounties(countyPopulations, ISOdate(2020,3,1, tz=""))
    subtext = "Data from NY Times via covid-19.datasettes.com"

```

## Covid in a Few Interesting Counties {.tabset} 

Covid case counts and death counts by county, based on daily data from NY Times via https://covid-19.datasettes.com

### Cases

```{r, selected_counties_cases, echo=FALSE, results='hide', message=FALSE,warning=FALSE}

    print(covidPlot(cases~date | county, data=selected, subtitle=subtext, group=state, main="Selected Counties"))
    
    print(covidPlot(100000*cases/county.population~date | county, data=selected, subtitle=subtext, group=state, main="Selected Counties",
          ylab="Cases per 100,000"))
    
    print(symmetricPlot(100000*case.slope/county.population~date | county, data=selected, group=selected$state, 
          subtitle = subtext, main="Selected Counties", 
          ylab="Slope (Cases/Day/100,000)",
          xlab="Date"))
    
    print(covidPlot(cases~date, data=selected, group=county, subtitle=subtext, main="Selected Counties",
        auto.key= list(cex=0.6, columns=3),
        par.settings= list(superpose.symbol=list(pch=1:25)) ))
    
    

```
        
### Deaths

```{r, selected_counties_deaths, echo=FALSE, results='hide', message=FALSE,warning=FALSE}    
    
    print(covidPlot(deaths~date | county, data=selected, subtitle=subtext, group=state, main="Selected Counties"))
    
    print(covidPlot(100000*deaths/county.population~date | county, data=selected, group=state, 
                            subtitle=subtext, ylab="Deaths per 100,000", main="Selected Counties"))

    
    print(symmetricPlot(death.slope ~ date | county, data=selected, group=selected$state, 
        subtitle = subtext, main="Selected Counties", 
        ylab="Slope (Deaths/Day)",
        xlab="Date"))

    
    print(symmetricPlot(100000*death.slope/county.population~date | county, data=selected, group=selected$state, 
        subtitle = subtext, main="Selected Counties", 
        ylab="Slope (Deaths/Day/100,000)",
        xlab="Date"))

    
    
    print(covidPlot(deaths~date, data=selected, group=county, subtitle=subtext, main="Selected Counties",
                            auto.key= list(cex=0.6, columns=3),
                            par.settings= list(superpose.symbol=list(pch=1:25)) ))
    

```

## Covid in All California Counties {.tabset}
Covid case counts and death counts by county, based on daily data from NY Times via https://covid-19.datasettes.com
```{r, california_counties, echo=FALSE, results='hide', message=FALSE,warning=FALSE}
    print(covidPlot(cases~date | county, data=ca, group=county, subtitle=subtext, main="California Counties"))
    print(covidPlot(deaths~date | county, data=ca, group=county, subtitle=subtext, main="California Counties"))
    print(covidPlot(100000*deaths/county.population~date | county, data=ca, group=county, subtitle=subtext, 
                            ylab="Deaths per 100,000", main="California Counties"))
    
    
    print(symmetricPlot(death.slope~date | county, data=ca, group=ca$county, 
        subtitle = subtext, main="California Counties", 
        ylab="Slope (Deaths/Day)",
        xlab="Date"))
    
    
     print(symmetricPlot(100000*death.slope/county.population~date | county, data=ca, group=ca$county, 
        subtitle = subtext, main="California Counties", 
        ylab="Slope (Deaths/Day/100,000)",
        xlab="Date"))
    
```

## Covid in All New York Counties {.tabset}
Covid case counts and death counts by county, based on daily data from NY Times via https://covid-19.datasettes.com
```{r, new_york_counties, echo=FALSE, results='hide', message=FALSE,warning=FALSE}
    print(covidPlot(cases~date | county, data=ny, group=county, subtitle=subtext, main="New York Counties"))
    print(covidPlot(deaths~date | county, data=ny, group=county, subtitle=subtext, main="New York Counties"))
    print(covidPlot(100000*deaths/county.population~date | county, data=ny, group=county, subtitle=subtext, 
                            ylab="Deaths per 100,000", main="New York Counties"))
    
```

## Covid in All Michigan Counties {.tabset}
Covid case counts and death counts by county, based on daily data from NY Times via https://covid-19.datasettes.com
```{r, michigan_counties, echo=FALSE, results='hide', message=FALSE,warning=FALSE}
    print(covidPlot(cases~date | county, data=mi, group=county, subtitle=subtext, main="Michigan Counties"))
    print(covidPlot(deaths~date | county, data=mi, group=county, subtitle=subtext, main="Michigan Counties"))
    print(covidPlot(100000*deaths/county.population~date | county, data=mi, group=county, subtitle=subtext, 
                            ylab="Deaths per 100,000", main="Michigan Counties"))
    
```


## Covid in US States {.tabset}
Covid positive tests, deaths, and hospitalizations by state from covidtracking.com https://covidtracking.com

### Hospitalizations

```{r,  state_hospital, echo=FALSE, results='hide', message=FALSE,warning=FALSE}
    source("covidtracking_us_states.r")
  print (p_hosp)
  print(p_hospPer)
```

### Positives

```{r,  state_positves, echo=FALSE, results='hide', message=FALSE,warning=FALSE}
    source("covidtracking_us_states.r")
  print(p_positives)
  print(p_positive_fraction)
  print(p_positivesPer)
  print (p_deltaPositivesPer)
```

### Deaths

```{r,  state_deaths, echo=FALSE, results='hide', message=FALSE,warning=FALSE}
    source("covidtracking_us_states.r")
  print(p_deaths)
  print (p_deathsPer)
  print(p_deltaDeathsPer)
    
```


## Covid in China {.tabset}

Covid data from Johns Hopkins CSSE via https://covid-19.datasettes.com
```{r,  china, echo=FALSE, results='hide', message=FALSE,warning=FALSE}
    source("covid_international.r")
    print(p_china)
    print(p_china_deaths)
```

## Covid in Scandanavia {.tabset}
```{r,  scandanavia, echo=FALSE, results='hide', message=FALSE,warning=FALSE}
  print(p_scandanavia)
  print(p_scandanavia_per)
  print(p_scandanavia_deaths)
  print(p_scandanavia_deaths_per)
```